---
title: "Interactive Exploration MultiGSEAResults with multiGSEA.shiny"
author: "Steve Lianoglou"
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('multiGSEA.shiny')`"
output:
  rmarkdown::html_document:
    self_contained: yes
    highlight: pygments
    toc: true
    fig_width: 5
vignette: >
  %\VignetteIndexEntry{Interactive Exploration MultiGSEAResults with multiGSEA.shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding[utf8]{inputenc}
---

# Overview

One of the main functionalities provided by the multiGSEA package is the
\code{multiGSEA} function itself which provides a container that holds the
results of the variety of gene set enrichement analyses performed by the
function as well as the differential expression results generated for the
sampe comparison.

This package provides a number of shiny modules that are stitched together
into an app invoked by the \code{explore} function which allows the user
to interactively explore the gene set enrichment analysis results from each
of the individual methods as well as the individual gene level differential
expression statistics.

You will first have to run `multiGSEA` on your dataset, or load a serialized
version of it from your disk:

```{r}
library(multiGSEA)
library(multiGSEA.shiny)
mg <- exampleMultiGSEAResult()
```

Then invoke the `explore` method to look at the results

```{r, eval=FALSE}
explore(mg)
```

Every bit of this application is interactive. Go ahead and play with it while
we expand on this documentation further ...


One piece of functionality that is non-obvious but quite useful is that when
you select genes (dots) on the various interactive plots that are generated,
a table is generated at the bottom of the application that lists the other
gene sets that those genes you selected are members of,
